---
title: "Vector & Matrix"
author: "Yunsheng Lu"
date: "2022-12-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

1. c( ): Concatenate numbers to create vector
2. x+y: sum of 2 vectors with the same length
3. length( ): check the length of the vector
```{r}
x<-c(1,3,2,5)
y<-c(2,3,4,6)
x
z<-x+y
z
length(x)
```

4. ls( ): list all the objects created so far
5. rm( ): remove the object chosen
(remove all the objects: rm(list=ls()) )
```{r}
ls()
rm(x,y)
ls()
```

6. rnorm( ): generate a verctor of random variables
7. cor( ): correlation of 2 vectors (n >= 3)
```{r}
a=rnorm(5,10,100)
b=a+rnorm(5,10,100) #second mean, third variance
cor(a,b)
```

8. set.seed( ): reproduce a previously generated set of random series
```{r}
set.seed(1)
rnorm(5)
set.seed(2)
rnorm(5)
set.seed(1)
rnorm(5)
```
--------------------------------------------------------------------------------

9. matrix( ): create a matrix given the form, given the entries
```{r}
x<-matrix(data=c(1,2,3,4),nrow=2,ncol=2)
x
y<-matrix(c(1,2,3,4),2,2) #default: byrow=FALSE
y
z1<-matrix(c(1,2,3,4),2,2,byrow=TRUE) #byrow means list entries in the row order
z1
```

10. sqrt( ): every entry of the vector/matrix taking the squared root
```{r}
sqrt(z)
sqrt(z1)
```

11. extract entries
```{r}
A<-matrix(1:16,4,4)
A
A[2,3]
A[c(1,3),c(2,4)] #c[1,3] refers to 1st and 3rd rows; c[2,4] refers to 2nd and 4th rows
A[1:3,2:4] #1:3: from 1st to 3rd rows; 2:4: from 2nd to 4th rows
A[1:3,] #default: full columns
A[c(1:2),]
A[1,]
A[,1:3] #default: full rows
```

12. remove entries
```{r}
B<-A[-c(1,3),]
B
```

13. dim( ): check the size of the matrix
```{r}
dim(A)
```