---
title: "Graphics"
author: "Yunsheng Lu"
date: "2022-12-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1.plot( ): plot a scatter plot of x against y.
```{r}
x<-rnorm(100)
y<-rnorm(100)
plot(x,y,xlab="x-axis",ylab="y-axis")
```

2.pdf(): create pdf
```{r}
pdf("Figure.pdf")
plot(x,y,col="green")
dev.off()
```

3.seq( ): create an interval with given steps
```{r}
x<-seq(-pi,pi,length=10)
x
```

4.contour( ): create 3d-plots
```{r}
y<-x
f<-outer(x,y,function(x,y) cos(y)/(1+x^2)) #a special use of outer( )
#cos(y)/(1+x^2), the value of the function, is the third coordinate
f #f here is a matrix whose entry is the function value of corresponding x,y
contour(x,y,f)
contour(x,y,f, nlevels=10)
fa<-(f-t(f))/2
contour(x,y,fa,col="lightgray", nlevels=15) #if add=TRUE, then the grey curve will be added to the previous graph
```

5.image( ): create colored 3d-plots
```{r}
image(x,y,fa)
persp(x,y,fa,theta=30)
persp(x,y,fa,theta=30,phi=40)
```

--------------------------------------------------------------------------------
Loading Data
```{r}
getwd()
setwd("/Users/luyunsheng/Desktop/Winter Stat ML")
Auto<-read.table("Auto.data",header=T,na.strings="?",stringsAsFactors=T)
```

6."$": We must use "$" to refer to a variable in a given data matrix
7.attach( ): setting a given data matrix to be the default (no need for "$")
8.as.factor( ): turn a numerical variable into categorical
```{r}
plot(Auto$year,Auto$mpg)
attach(Auto)
plot(cylinders,mpg)
cylinders<-as.factor(cylinders)
plot(cylinders,mpg) #when plotting categorical variable, the default is boxplot
```

9. varwidth=T: adjust the width of the box to the sample size
```{r}
plot(cylinders,mpg,varwidth=T)
plot(cylinders,mpg,col="blue", varwidth=T, xlab="cylinders", ylab="MPG")
```

10. hist( ): plot histagram
```{r}
hist(mpg)
hist(mpg,col=2)
hist(mpg,col=2,breaks=15) #break denotes the number of cut-off points for a histagram
```

11. pairs( ): create scatterplot for every pair of variables (also called scatterplot matrix)
```{r}
pairs(Auto)
pairs(~mpg+displacement+weight,data=Auto) #sub-scatterplot matrix
```

12. identify(): identify the value/other properties of a point on a scatter plot
```{r}
plot(horsepower,mpg)
identify(horsepower,mpg,name) #works for console. if clicked, the point will show the associated name
identify(horsepower,mpg,n=3) #If clicked, up to 3 points will show the associated value of mpg

```