---
title: "Loading Data"
author: "Yunsheng Lu"
date: "2022-12-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
```{r}
getwd()
setwd("/Users/luyunsheng/Desktop/Winter Stat ML")
Auto<-read.table("Auto.data")
View(Auto) #type in console to view Auto as a spreadsheet in a new r-studio window 
head(Auto) #works for R Markdown
```


1. header=T means the first line of the data denotes the variable name
2. na.strings="?" means whenever R meets "?", the entry should be seen as a missing element in the data matrix
3. stringsAsFactors=T means whenever a variable containing character string should be treated as qualitive
```{r}
Auto<-read.table("Auto.data",header=T,na.strings="?",stringsAsFactors=T)
head(Auto)
```

4. dim( ): row represents # of observations and columns represents # of variables
5. names( ): check variable's name
```{r}
dim(Auto)
Auto[1:4,]
Auto<-na.omit(Auto) #data matrix with NA omitted
Auto
dim(Auto)
names(Auto)
```

6. "$": We must use "$" to refer to a variable in a given data matrix
7.attach( ): setting a given data matrix to be the default (no need for "$")
8.as.factor( ): turn a numerical variable into categorical
```{r}
plot(Auto$year,Auto$mpg)
attach(Auto)
plot(cylinders,mpg)
cylinders<-as.factor(cylinders)
plot(cylinders,mpg) #when plotting categorical variable, the default is boxplot
```

9. varwidth=T: adjust the width of the box to the sample size
```{r}
plot(cylinders,mpg,varwidth=T)
plot(cylinders,mpg,col="blue", varwidth=T, xlab="cylinders", ylab="MPG")
```

10. summary( ): provide a numerical summary of each variable in a data matrix
```{r}
summary(Auto)
summary(mpg)
```

